### 2019-01-13 papers/journal/experiments.tex
SAT SMT table update
Added Biological Interpretation to the REsult section

All the experiments were done
%Each test was run 
on a machine with Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM.
%
A 90 min (5400 sec) timeout was used for the tool.

@@

The minimal connectivity results for each variation of the existential condition are presented in table~\ref{tab:smt-grph}.
%
%No matter what the rules of molecular interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
The steady-state constraint requires that structure of the graph is at least 2-connected. 
%
We found that 3-connectedness is the existential condition for the Boolean regulation model on vesicles, while 4-connectedness is the existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%
For all other constrained regulation models of VTS, the experimentation was unable to find any graphs representing the vesicle transport networks in the stable state.
%(including the case where SNAREs are always active) we did not find any possible graphs representing stable vesicle transport networks. 
%
This hints that no such graphs exist, as our graphs are of finite size, this does not amount to a  proof. 
%This strongly suggests (but does not prove, since we only checked graphs of finite size) that no such graphs exist.
%We have found no graphs for Variants A where no regulation is enforced on the activity of the molecules both on the edges and nodes.
%%
%Two other cases Variant B, Variant E also results in the no graph satisfying the constraints.
%%  
%2-connectedness is the existential condition for Variants D where activity of the molecule is dependent on the presence of the other molecules. 
%%
%Variants C has 3-connectedness as

@@

\input{qbf-table}
%\textbf{Universal Condition:}
\todo{SA: will improve after experimentation.}
Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
%
The table represents the result of the graph connectivity for each variation of the VTS.  
%
For example, we found that the 3-connected graph satisfies the universal condition for the variation 2. 
%
Note that for this variation existential condition result was the 2-connected graph. 
%
For every other version, the results remained the same.
% 
The experimentations were done using two QBF solvers: \depqbf and \rarqbf.

>>>>

All the experiments were done
%Each test was run 
on a machine with Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM.
%
A 120 min (7200 sec) timeout was used for the tool.

@@

The minimal connectivity results for each variation of the existential condition are presented in table~\ref{tab:smt-grph}.
%
%No matter what the rules of molecular interactions and regulation, steady state requires the graph structure to be at least strongly connected, and therefore 2-connected.
The steady-state constraint requires that structure of the graph is at least 2-connected. 
%
We found that 3-connectedness is the existential condition for the Boolean regulation model on vesicles, while 4-connectedness is the existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%Beyond this, we find that 3-connectedness is existential condition for the Boolean regulation model on vesicles, while 4-connectedness is existential condition for the more constrained SNARE-SNARE inhibition on vesicles and Boolean regulation on compartments.
%
For all other constrained regulation models of VTS, the experimentation was unable to find any graphs representing the vesicle transport networks in the stable state.
%(including the case where SNAREs are always active) we did not find any possible graphs representing stable vesicle transport networks. 
%
This strongly suggests that no such graphs exist, as our graphs are of finite size, this does not amount to a  proof.

For biological cells, the steady state condition implies that every compartment that gives a vesicle necessarily receives a vesicle too.
%
On top of this, for the case where traffic molecules are regulated in some form, every pair of compartments with a vesicle going between them, have two additional vesicle paths connecting them; where these two paths go in opposite directions.
%
Finally, when we take into account the exact manner in which SNAREs interact in real cells, we find that the biological VTS must conform to a very specific structure; any two compartments that are connected by a vesicle, must be connected by 4 vesicle paths, two of them going in the same direction, and the other two in the opposite direction. 
%
No graph results suggests that a functional VTS necessarily needs some form of regulation, where the molecules of the VTS are kept inactive in places where they might disrupt other interactions

%This strongly suggests (but does not prove, since we only checked graphs of finite size) that no such graphs exist.
%We have found no graphs for Variants A where no regulation is enforced on the activity of the molecules both on the edges and nodes.
%%
%Two other cases Variant B, Variant E also results in the no graph satisfying the constraints.
%%  
%2-connectedness is the existential condition for Variants D where activity of the molecule is dependent on the presence of the other molecules. 
%%
%Variants C has 3-connectedness as

@@

\input{qbf-table}
%\textbf{Universal Condition:}

Table~\ref{tab:qbf-graph} presents the result of the QBF tool.
%
The table represents the result of the graph connectivity for each variation of the VTS.  
%
For example, we found that the 3-connected graph satisfies the universal condition for the variation 2. 
%
Note that for this variation existential condition result was the 2-connected graph. 
%
For every other version, the results remained the same.
This implies that for every 3-connected graph, a valid VTS that satisfies all constraints \todo{ elaborate a bit on the constraints} exists.
% 
For biological cells, this means that the whole space of 3-connected graphs is available for evolutionary exploration
%
%The experimentations were done using two QBF solvers: \depqbf and \rarqbf.
